\documentclass{resume} 
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Daniel Tellier}
\career{Software Engineer}
\address{(818) 274-2301 | telldanieljames@gmail.com | Los Angeles, CA} 

\begin{document}

\begin{rSection}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Languages & C/C++, Python, Java, C\#, MySQL, MATLAB, Bash, Tcl  \\
    Tools & DataGrip, Agile Development, VSCode, Visual Studio, Unity Game Engine, CUDA \\
    Cloud Technologies & AWS, Google Cloud \\
    Version Control & Git, GitHub \\
    Operating Systems & Linux, Windows \\
    \end{tabular}
\end{rSection}

\begin{rSection}{Employment}
    \begin{rSubsection}{Northrop Grumman - Los Angeles, CA}{June 2020 - Current}{Software Engineer}{}
        \item Automated the official testing for the flight management system (FMS) on the Black Hawk Helicopter
        \item Improved the test scripts run time by finding a pointless socket sending messages every cycle. \hfill \break
        Once this socket was prevented from running a test script running 10K cycles ran 3 minutes rather \hfill \break
        than 12 minutes. Now the roughly 220 test scripts for FMS take 5.5 hours rather than 25 hours to run.
        \item Organized the flight management system test script library
        \item Generated graphs for analyzing the performance of a partition or application on the Black Hawk
    \end{rSubsection}
    \begin{rSubsection}{nFlux AI - Los Angeles, CA}{Sept. 2019 - May 2020}{Software Engineer Intern}{}
        \item Trained robot to learn soccer in 2D simulation using imitation learning
        \item Robot reached 94 percent accuracy in scoring goals
    \end{rSubsection}
    \begin{rSubsection}{CSUN TAVLAB - Los Angeles, CA}{Aug. 2019 - June 2020}{Software Engineer Intern}{}
        \item Designed programming language prototype for JPL
        \item The language called Proteus is meant to simplify the process of writing hierarchical state machines
    \end{rSubsection}
    \begin{rSubsection}{Northrop Grumman - Los Angeles, CA}{June 2019 - Aug. 2019}{Software Engineer Intern}{}
        \item Developed software for aircraft navigational systems to meet current FAA standards
        \item Designed test scripts to ensure algorithm accuracy
        \item Auto generated C++ to be utilized in flight critical systems
    \end{rSubsection}
    \begin{rSubsection}{Shiva - Los Angeles, CA}{June 2018 - June 2019}{Software Engineer Intern}{}
        \item Utilized machine learning in soccer simulation
        \item Performed supervised learning on simulation to speed up training time
        \item Increased experience generation of simulation by 20\%
        \item Developed in Pytorch using Multi-GPU capabilities with CUDA
    \end{rSubsection}
    \begin{rSubsection}{Systems Engineering Research Lab - Los Angeles, CA}{June 2018 - Dec. 2018}{Software Engineer Intern}{}
        \item SERL collaborates with the US Air Force and LA Fire Department
        \item Designed parts of simulation to detect humans in a hazardous building
        \item Utilized Agile Development to produce software and led Scrum meetings
        \item Graphically represented over 20 features of the simulation
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Education}
    {\bf CSU Northridge} \hfill {\em Jan. 2015 - May 2020} 
    \\ B.S. Computer Science \hfill { Overall GPA: 3.6 }
    \\ Dean's List \hfill {Spring 2015, Fall 2015, Fall 2016}
    \\ Courses \hfill {Machine Learning, Data Mining, Data Structures, Statistics}
\end{rSection}

\end{document}